---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ5SkBQeWi3vD2icrzUBCJTR7hG80l7d5WwMMG5OD3SUDryC5z0oYL2kTv2eL9SV4Ou6MHnwj7HTHDV/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    ad_type = 2,
    frequency_per_week = 3,
    brand_names = 4
  ) %>%
  mutate(frequency_per_week = as.numeric(frequency_per_week))

# Summary values
num_responses <- nrow(latest_data)
mean_frequency <- mean(latest_data$frequency_per_week, na.rm = TRUE)
max_frequency <- max(latest_data$frequency_per_week, na.rm = TRUE)
min_frequency <- min(latest_data$frequency_per_week, na.rm = TRUE)
```


```{css}
body {
  font-family: "Helvetica Neue", Helvetica, Arial, sans-serif;
  line-height: 1.6;
  color: #333;
  background-color: #f9f9f9;
  padding: 1rem;
}

h2 {
  color: #1e90ff;
  border-bottom: 2px solid #ddd;
  padding-bottom: 0.3rem;
}

p {
  margin-bottom: 1rem;
}

img {
  max-width: 100%;
  height: auto;
}

.plot-title {
  color: #444;
  font-size: 1.2rem;
  margin-top: 2rem;
}
```

## What is this data about?
This report explores the types, frequency and branding of YouTube ads based on survey responses collected using a Google form.

I analysed `r num_responses` responses to understand what kind of ads are most frequently shown, how often people see them each week, and which brands are appearing the most.

## Ad Frequency Insights
The average number of ads users encounter from their most frequent ad category in a week is `r mean_frequency`. The minimum reported frequency is `r min_frequency`, and the maximum is `r max_frequency`.

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = frequency_per_week), fill = "tomato") +
  labs(
    title = "How Frequently Ads Appear in a Week",
    x = "Ads per Week",
    y = "Count"
  )
```

## Most Recommended Ad Types
The bar chart below shows the distribution of ad categories most frequently recommended to survey participants.

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = ad_type), fill = "lightblue") +
  labs(
    title = "Most Frequently Recommended Ad Types on YouTube",
    x = "Ad Type",
    y = "Count"
  )
```

## Brands Appearing Most Often
Here are the brand names most often associated with the ads users see:

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = brand_names), fill = "lightgreen") +
  labs(
    title = "Brands Mentioned in YouTube Ads",
    x = "Brand",
    y = "Count"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

